Titeln på avhandlingens språk

### 2022-11-07 background.tex
tweaking

Current implementations, such as those in~\cite{Chen2015LEGO,Chen2018application}, employ \emph{greedy} sampling.
In this scheme, a new sample is immediately taken as soon as an acknowledgement is received for the previous sample.
This means that the interval between these sampling instants is not necessarily constant, as it is subject to fluctuations due to resource contention on both the network and compute side.
It also has as a consequence that acknowledgements must be provided even for those samples which do not cause the generation of a new instruction --- these acknowledgements are simply used for flow control and do not generate user-noticeable feedback.

Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling intervals (following a greedy scheme) at which the \ac{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e. which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
If we define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), it must follow that (see also~\cite{olguinmunoz:impact2021})\footnote{\( U(a, b) \) represents the continuous uniform distribution in the open interval \( (a, b) \).}
% \todo[inline]{I think it's an assumption rather than a must. Specifically, it is not uniform if the general execution time distribution is Rayleigh/ExpGaussian -vishnu}
\begin{align}\label{eq:tc}
    t_c &\thicksim U(t_{n - 1}, t_n)
\end{align}

We define the intervals \( t_c - t_0 \), \( t_n - t_c \), and \( t_{n + 1} - t_n \) as the \emph{execution time}, \emph{wait time}, and \emph{last sample \ac{RTT}}, respectively, of a step \( M \).
The sum of the latter two values (i.e. the interval \( t_{n + 1} - t_c \)) we call \emph{\ac{TTF}}.
Once again, refer to \cref{fig:step} for a visual breakdown of these values.

@@

For this work, we used \emph{delay} and execution time as the variables for system responsiveness and human behavior, respectively.
\emph{Delay} corresponded to a temporarily fixed time duration of the processing of each frame was padded to --- i.e. if during a series of steps delay was set to \( D \) seconds, the feedback for each frame was provided to the user at exactly \( D \) seconds after frame capture.
The correlation between this variable and execution time was then studied.
Delay, however, was merely an experimental tool, and if we consider
\begin{enumerate*}[itemjoin={{; }}, itemjoin={{; and }}]
    \item \cref{eq:tc} above
    \item that for a step subject to delay \( D \), \( t_k - t_{k - 1} = D \) for all \( k \in \{1, 2, \ldots, n\} \)
\end{enumerate*},
then it follows that, \emph{on average}, for \emph{all} steps subject to a delay \( D \):

\begin{align}\label{eq:ttf}
    \text{\emph{\ac{TTF}}} = \frac{3}{2}D
\end{align}

>>>>

As expressed above, \acp{WCA} employ sampling, most commonly of video feeds, to keep track of the state of the real world.
Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling instants at which the \ac{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e.\ which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
We define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), and the intervals \( t_c - t_0 \), \( t_n - t_c \), and \( t_{n + 1} - t_n \) as the \emph{execution time}, \emph{wait time}, and \emph{last sample \ac{RTT}}, respectively, of a step \( M \) (once again, refer to \cref{fig:step} for a visual breakdown of these values).
The sum of the latter two values (i.e.\ the interval \( t_{n + 1} - t_c \)) we call \emph{\ac{TTF}}, a metric which we will repeatedly refer to in this paper as it directly describes the responsiveness of a \ac{WCA}.

% It should be noted 
% it must follow that (see also~\cite{olguinmunoz:impact2021})\footnote{\( U(a, b) \) represents the continuous uniform distribution in the open interval \( (a, b) \).}
% % \todo[inline]{I think it's an assumption rather than a must. Specifically, it is not uniform if the general execution time distribution is Rayleigh/ExpGaussian -vishnu}
% \begin{align}\label{eq:tc}
%     t_c &\thicksim U(t_{n - 1}, t_n)
% \end{align}

% Current implementations, such as those in~\cite{Chen2015LEGO,Chen2018application}, employ \emph{greedy} sampling.
% In this scheme, a new sample is immediately taken as soon as an acknowledgement is received for the previous sample.
% This means that the interval between these sampling instants is not necessarily constant, as it is subject to fluctuations due to resource contention on both the network and compute side.
% It also has as a consequence that acknowledgements must be provided even for those samples which do not cause the generation of a new instruction --- these acknowledgements are simply used for flow control and do not generate user-noticeable feedback.

@@

For this work, we used \emph{delay} and execution time as the variables for system responsiveness and human behavior, respectively.
\emph{Delay} corresponded to a temporarily fixed time duration of the processing of each frame was padded to --- i.e.\ if during a series of steps delay was set to \( D \) seconds, the feedback for each frame was provided to the user at exactly \( D \) seconds after frame capture.
The correlation between this variable and execution time was then studied.
Delay, however, was merely an experimental tool, and if we consider
\begin{enumerate*}[itemjoin={{; }}, itemjoin={{; and }}]
    \item that \( t_c \), and conversely the wait time \( \mathcal{W} \) of a step, can be assumed to be uniformly distributed in the interval \( [t_{n - 1}, t_n] \) without loss of generality~\cite{olguinmunoz:impact2021}
    \item that for a step subject to delay \( D \), \( t_k - t_{k - 1} = D \) for all \( k \in \{1, 2, \ldots, n\} \)
\end{enumerate*},
then it follows that the expected \ac{TTF} for steps subject to a delay \( D \) can be expressed as

\begin{align}
    \mathbb{E}\left[\text{\ac{TTF}}\right] &= \mathbb{E}\left[\mathcal{W}\right] + D
    = \mathbb{E}\left[U(t_{n - 1}, t_n)\right] + D\nonumber\\
    &= \mathbb{E}\left[U(0, D)\right] + D
    = \frac{1}{2}D + D = \frac{3}{2}D\label{eq:ttf}
\end{align}

### 2022-11-07 implications_footprint.tex
tweaking

\section{Implications for the study of \ac{WCA} footprints}\label{sec:implications:footprint}
\todo[inline]{Two subsections (simulation and real system.)}
\todo[inline]{Leave it for now.}
% \todo[inline]{Introduction to this section?}

\subsection{Application lifetimes}

We begin by studying the implications of such a model on the estimation of application lifetimes.
In the context of \ac{WCA}, we will understand \emph{application lifetime} as the time it takes a user to complete a specified task.
This is an important metric for \ac{WCA} optimization, as it directly relates to system resource utilization and contention, and to energy consumption.

@@

Next we study the effects of first- versus second-order models in a more realistic setting.
The models, reference and realistic, are deployed on the Raspberry Pi clients of the testbed depicted in \cref{fig:expsetup}.
For this, the timing models and frame generator are integrated into a custom Python3 client for the Gabriel \ac{WCA} platform~\cite{Chen2018application}, which are then paired with real instances of Gabriel deployed on the cloudlet.
Clients and cloudlet communicate over an \acs{IEEE} \num{802.11}b/g wireless network.
Our choice of wireless standard is simply motivated by a desire to amplify the potential effects of network congestion.
\todo[inline]{More justification?}

@@

\todo[inline]{%
    Ergo we need a second order model. Everything that comes afterwards is only with second order model. Play with RTT.
}

>>>>

\section{Implications for the study of \ac{WCA} footprints}\label{sec:implications:footprint}

% \subsection{Application lifetimes}

We begin by studying the implications of such a model on the estimation of application footprints as described by their lifetimes.
In the context of \ac{WCA}, we will understand \emph{application lifetime} as the time it takes a user to complete a specified task.
This is an important metric for \ac{WCA} optimization, as it directly relates to system resource utilization and contention, and to energy consumption.

@@

Next we study the effects of first- versus second-order models in a more realistic setting.
The models, reference and realistic, are deployed on the Raspberry Pi clients of the testbed depicted in \cref{fig:expsetup}.
For this, the timing models and frame generator are integrated into a custom Python3 client for the Gabriel \ac{WCA} platform~\cite{Chen2018application}, which are then paired with real instances of Gabriel deployed on the cloudlet.
Clients and cloudlet communicate over an \acs{IEEE} \num{802.11}b/g wireless network.
Our choice of wireless standard is simply motivated by a desire to amplify the potential effects of network congestion.

@@

% \todo[inline]{%
%     Ergo we need a second order model. Everything that comes afterwards is only with second order model. Play with RTT.
% }

### 2022-11-07 implications_optimization.tex
tweaking

\todo[inline]{Finish}

@@

Again, our optimization approach focuses on individual steps.
Thus, we begin by assuming a given execution time distribution \( \mathcal{T} \), and take the modeling and partial solution approach from recents works on energy efficient sampling in edge-based feedback systems.
In \textcite{ICCperiodic1,TMCperiodic}, the authors model the energy in terms of the expected number of samples $\mathbb{E}[\mathcal{S}]$ and the expected wait time $\mathbb{E}[\mathcal{W}]$ experienced by the user.
The authors then find the optimum periodic sampling interval that minimizes this energy, or equivalently the non-constant parts of this energy termed as \textit{Energy Penalty}.

% In this optimization, the constant parts are excluded as it does not affect the process.
With a value much smaller than the execution time of the event, the \ac{RTT} of the final sample is included in this constant part, which is why $\mathcal{W}$ is computed without it.
Next, in \textcite{secAperiodic}, the author retains the model, removes the constraint of periodicity, and finds the optimum aperiodic sampling instants $\{t_n,\,n=1,2,\dots\}$ that minimize the same energy penalty.

In this work, we use the modeling from~\cite{secAperiodic} to find the optimum \emph{aperiodic} sampling interval.
However, instead of using their two-step approach to find the solution which includes a recursive solution followed by a bisection algorithm, we develop a novel, approximate, but easier solution to finding the set of the optimum aperiodic sampling intervals.
Furthermore, instead of directly optimizing for energy, we start by noting that an objective metric of a variety of optimization problems that are related to sampling, RTT, responsiveness or wait time present themselves 
% in a format similar to that of the energy, 
as a linear combination between $\mathbb{E}[\mathcal{S}]$ and $\mathbb{E}[\mathcal{W}]$ plus terms independent of the number of samples or wait time.
Let $\mathcal{E}$ correspond to such an objective metric.
Thus,
\begin{alignat}{1}
    \Rightarrow\mathcal{E}&=\alpha\mathbb{E}[\mathcal{S}]+\beta\mathbb{E}[\mathcal{W}]+C,\;\label{eq:epsilon_terminal}
\end{alignat}
\todo[inline]{
Optimization is own section.    
First thing in optimization. Represents a lot of tradeoffs in these systems. For two particular metrics, we discuss solutions of this equations for different optimization purposes. We compare to other approaches. State of the art and offline optimum.
Optimization business should go into own section.}
Here, $\alpha, \beta$ and $C$ are constants which are responsible for modifying the objective function from one metric to another.
For instance, in the modeling used by \textcite{ICCperiodic1,TMCperiodic,secAperiodic}, the chosen characterization results in a metric which is equal to the energy penalty.
The outline of our solution that minimizes \cref{eq:epsilon_terminal} is provided below with the complete mathematical derivation in \cref{appx1}.

@@

Define an instantaneous sampling rate function $r(t)$ which is related to $\{t_n\}$ such that,
\begin{alignat}{1}
{\int_{t_{n-1}}^{t_n}}r(t)\dif t=1,\;\forall n\geq1.\label{rt}
\end{alignat}
For instance, for periodic sampling, the rate function is a constant equal to the sampling frequency. 
% Using this rate function, we rewrite the expected number of samples as
% \begin{alignat}{1}
% \mathbb{E}[\mathcal{S}]&=\int_{t=0}^{\infty}\bigg(\!\int_{x=0}^{t}\!\!\!\!r(x)\,\mathrm{d}x\bigg)f_{\mathcal{T}}(t)\,\mathrm{d}t,\nonumber
% \end{alignat}
% and the approximate the expected wait time as
% \begin{alignat}{1}
% \mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber
% \end{alignat}
Now, rewriting \cref{eq:epsilon_terminal} in terms of $r(t)$ and minimizing it gives as an optimum rate function $r^*(t)$ as
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}.\nonumber\\
\intertext{Thus, for a Rayleigh distributed $\mathcal{T}$ with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\nonumber\\
% \Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
% \Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\Rightarrow t_n&=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tn_approx_rayleigh}
\end{alignat}

@@

In the following we thus take the general solution, \cref{eq:epsilon_terminal}, and find the appropriate \( \alpha \) and \( \beta \) to minimize the energy consumed per step, i.e.\ \( \mathcal{E}=E \).
We directly take the modeling from~\cite{secAperiodic} with a necessary modification in the assumption of one-way communication in all but the final sample.
With feedback given even to the discarded samples in our model, we have, 
\begin{alignat}{2}
    \mathrm{E}=&\;2\mathcal{S}\tau_cP_c+(\mathcal{T}+\mathcal{W}+\tau_\mathrm{p}+2\tau_\mathrm{c}-2\mathcal{S}\tau_c)P_0\nonumber\\
    % &=s\tau_c(P_c-P_0^{(t)})+wP_0^{(t)}+(\tau+\tau_c+\tau_p) P_0^{(t)}+\tau_cP_c\\
    =&\;2\tau_{\text{c}}(P_{\text{c}} -P_0)\mathcal{S}+\mathcal{W}P_0+(\mathcal{T}+\tau_{\text{p}} +2\tau_{\text{c}}) P_0\nonumber\\
&\Rightarrow \alpha=2\tau_{\text{c}}(P_{\text{c}} -P_0),\text{ and }\beta=P_0 \label{eq:optimization:energy}
\end{alignat}
\( \tau_\text{p} \) and \( \tau_\text{c} \) correspond to the processing and communication delay for each sample.
\( P_\text{c} \) and \( P_0 \) correspond to the communication and idle power, respectively, of the \ac{WCA} client device.

We proceed to repeat the experiment detailed in \cref{ssec:optimization:samples}, replacing the sample-count-optimized sampling scheme with a new implementation instead minimizing energy, using \cref{eq:optimization:energy} for the calculation of \( \alpha \) and \( \beta \).
Once again, we embed a timing model into the sampling scheme to provide updated estimates of the mean execution time \( \mu \) at each step.
We refer to this scheme as the \emph{energy-optimized aperiodic} sampling scheme.
For the power constants, we reuse the values estimated by the authors in \textcite{TMCperiodic}, \( P_\text{c} = 45\,\si{\milli\watt} \) and \( P_\text{0} = 15\,\si{\milli\watt} \).
On the other hand, for the timing variables we define a constant processing delay \( \tau_\text{p} = 250\,\si{\milli\second} \) across all configurations and repetitions of the experiments; given then a constant \ac{RTT} for the task, we set \( \tau_\text{c} = \text{\ac{RTT}} - \tau_\text{p} \).

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization.png}
        \caption{}
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization_diff.png}
        \caption{}
    \end{subfigure}
    \caption{Energy optimization}\label{fig:optimization:energy}
\end{figure*}

>>>>

% \todo[inline]{Finish}

@@

Our optimization approach focuses on the individual steps which comprise a complete \ac{WCA} task.
Thus, we begin by assuming a given execution time distribution \( \mathcal{T} \), and take the modeling and partial solution approach from recents works on energy efficient sampling in edge-based feedback systems.
In \textcite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient}, the authors model the energy in terms of the expected number of samples $\mathbb{E}[\mathcal{S}]$ and the expected wait time $\mathbb{E}[\mathcal{W}]$ experienced by the user.
The authors then find the optimum periodic sampling interval that minimizes this energy, or equivalently the non-constant parts of this energy termed as \textit{Energy Penalty}.

% In this optimization, the constant parts are excluded as it does not affect the process.
With a value much smaller than the execution time of the event, the \ac{RTT} of the final sample is included in this constant part, which is why $\mathcal{W}$ is computed without it.
Next, in \textcite{Moothedath2022Aperiodic}, the author retains the model, removes the constraint of periodicity, and finds the optimum aperiodic sampling instants $\{t_n,\,n=1,2,\dots\}$ that minimize the same energy penalty.

In this work, we use the modeling from~\cite{Moothedath2022Aperiodic} to find the optimum \emph{aperiodic} sampling interval.
However, instead of using their two-step approach to find the solution which includes a recursive solution followed by a bisection algorithm, we develop a novel, approximate, but easier solution to finding the set of the optimum aperiodic sampling intervals.
Furthermore, instead of directly optimizing for energy, we start by noting that an objective metric of a variety of optimization problems that are related to sampling, RTT, responsiveness or wait time present themselves 
% in a format similar to that of the energy, 
as a linear combination between $\mathbb{E}[\mathcal{S}]$ and $\mathbb{E}[\mathcal{W}]$ plus terms independent of the number of samples or wait time.
Let $\mathcal{E}$ correspond to such an objective metric.
Thus,
\begin{alignat}{1}
    \Rightarrow\mathcal{E}&=\alpha\mathbb{E}[\mathcal{S}]+\beta\mathbb{E}[\mathcal{W}]+C,\;\label{eq:epsilon_terminal}
\end{alignat}

Above, $\alpha, \beta$ and $C$ are constants which are responsible for modifying the objective function from one metric to another.
For instance, in the modeling used by \textcite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient,Moothedath2022Aperiodic}, the chosen characterization results in a metric which is equal to the energy penalty.
The outline of our solution that minimizes \cref{eq:epsilon_terminal} is provided below with the complete mathematical derivation in \cref{appx1}.

@@

We first define an instantaneous sampling rate function $r(t)$ which is related to $\{t_n\}$ such that,
\begin{alignat}{1}
{\int_{t_{n-1}}^{t_n}}r(t)\dif t=1,\;\forall n\geq1\label{rt}
\end{alignat}
For instance, for periodic sampling, the rate function is a constant equal to the sampling frequency. 
% Using this rate function, we rewrite the expected number of samples as
% \begin{alignat}{1}
% \mathbb{E}[\mathcal{S}]&=\int_{t=0}^{\infty}\bigg(\!\int_{x=0}^{t}\!\!\!\!r(x)\,\mathrm{d}x\bigg)f_{\mathcal{T}}(t)\,\mathrm{d}t,\nonumber
% \end{alignat}
% and the approximate the expected wait time as
% \begin{alignat}{1}
% \mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber
% \end{alignat}
Next, rewriting \cref{eq:epsilon_terminal} in terms of $r(t)$ and minimizing it gives as an optimum rate function $r^*(t)$ as
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}\nonumber\\
\intertext{in turn resulting in, for a $\mathcal{T}$ distributed according to a Rayleigh distribution with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\nonumber\\
% \Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
% \Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\Rightarrow t_n&=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tn_approx_rayleigh}
\end{alignat}

@@

In the following we thus take the general solution, \cref{eq:epsilon_terminal}, and find the appropriate \( \alpha \) and \( \beta \) to minimize the energy consumed per step, i.e.\ \( \mathcal{E}=E \).
We directly take the modeling from~\cite{Moothedath2022Aperiodic} with a necessary modification in the assumption of one-way communication in all but the final sample.
With feedback given even to the discarded samples in our model, we have, 
\begin{alignat}{2}
    \mathrm{E}=&\;2\mathcal{S}\tau_cP_c+(\mathcal{T}+\mathcal{W}+\tau_\mathrm{p}+2\tau_\mathrm{c}-2\mathcal{S}\tau_c)P_0\nonumber\\
    % &=s\tau_c(P_c-P_0^{(t)})+wP_0^{(t)}+(\tau+\tau_c+\tau_p) P_0^{(t)}+\tau_cP_c\\
    =&\;2\tau_{\text{c}}(P_{\text{c}} -P_0)\mathcal{S}+\mathcal{W}P_0+(\mathcal{T}+\tau_{\text{p}} +2\tau_{\text{c}}) P_0\nonumber\\
&\Rightarrow \alpha=2\tau_{\text{c}}(P_{\text{c}} -P_0),\text{ and }\beta=P_0 \label{eq:optimization:energy}
\end{alignat}
\( \tau_\text{p} \) and \( \tau_\text{c} \) correspond to the processing and communication delay for each sample.
\( P_\text{c} \) and \( P_0 \) correspond to the communication and idle power, respectively, of the \ac{WCA} client device.

We proceed to repeat the experiment detailed in \cref{ssec:optimization:samples}, replacing the sample-count-optimized sampling scheme with a new implementation instead minimizing energy, using \cref{eq:optimization:energy} for the calculation of \( \alpha \) and \( \beta \).
Once again, we embed a timing model into the sampling scheme to provide updated estimates of the mean execution time \( \mu \) at each step.
We refer to this scheme as the \emph{energy-optimized aperiodic} sampling scheme.
For the power constants, we reuse the values estimated by the authors in \textcite{Moothedath2022EnergyEfficient}, \( P_\text{c} = 45\,\si{\milli\watt} \) and \( P_\text{0} = 15\,\si{\milli\watt} \).
On the other hand, for the timing variables we define a constant processing delay \( \tau_\text{p} = 250\,\si{\milli\second} \) across all configurations and repetitions of the experiments; given then a constant \ac{RTT} for the task, we set \( \tau_\text{c} = \text{\ac{RTT}} - \tau_\text{p} \).

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization.png}
        \caption{%
            Round-trip time versus mean per step energy consumption, averaged over all \num{100} repetitions of the experiment.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization_diff.png}
        \caption{%
            Percentage difference in mean per step energy consumption with respect to the greedy sampling scheme.
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the energy-optimized aperiodic sampling scheme to the reference schemes and \textcite{Wang2019Towards}'s \ac{CDF}-based approach.
    }\label{fig:optimization:energy}
\end{figure*}

### 2022-11-07 intro.tex
tweaking

With that context, we can express the contributions of this paper as follows:
\begin{enumerate}
    \item\label{item:contrib:model} We introduce the first, to our knowledge, data-driven model for human timings in \ac{WCA} applications.
    Using the data collected for \textcite{olguinmunoz:impact2021} as a base, we build a stochastic model which takes as input past measurements of system responsiveness and produces realistic step execution times.
    \item\label{item:contrib:frames} We introduce a novel way to generate dynamic traces of frames for \ac{WCA} applications which can be combined with the timing model for a full end-to-end emulation of a human.
    \item Finally, using \cref{item:contrib:model,item:contrib:frames}, we explore the potential for optimization in these systems, and propose a novel strategy for the optimum sampling of \ac{WCA} applications with respect to the number of video frames captured per step.
\end{enumerate}

@@

\todo[inline]{%
Nice intro. Perhaps too long, and a concise presentation - preferably as bullet list - of the contributions is missing. Try to shorten in particular for the first three paragraphs. Another question would be if there is no other related work. For instance, Zorzi recently published a model for AR and VR - trace-based - that would be a good reference to have. 
}

>>>>

With that context, we can express the contributions of this paper as follows:
\begin{enumerate}
    \item\label{item:contrib:model} We introduce the first, to our knowledge, data-driven model for human timings in \ac{WCA} applications.
    Using the data collected for \textcite{olguinmunoz:impact2021} as a base, we build a stochastic model which takes as input past measurements of system responsiveness and produces realistic step execution times.
    We also introduce a novel way to generate dynamic traces of frames for \ac{WCA} applications which can be combined with the timing model for a full end-to-end emulation of a human.
    \item Using \cref{item:contrib:model}, we explore the potential for optimization in these systems, and propose a novel stochastic optimization framework for resource consumption-system responsiveness trade-offs in \ac{WCA}.
    This framework is applicable to a number of optimization purposes in \ac{WCA}, and we demonstrate its use for two relevant ones: number of samples captured per step and energy consumed per step.
\end{enumerate}

@@

\todo[inline]{%
Shorten.
Include Zorzi et al. AR VR
}
